---
title: "Mini Data Analysis Milestone 2"
output: github_document
---

*To complete this milestone, you can either edit [this `.rmd` file](https://raw.githubusercontent.com/UBC-STAT/stat545.stat.ubc.ca/master/content/mini-project/mini-project-2.Rmd) directly. Fill in the sections that are commented out with `<!--- start your work here--->`. When you are done, make sure to knit to an `.md` file by changing the output in the YAML header to `github_document`, before submitting a tagged release on canvas.*

# Welcome to the rest of your mini data analysis project!

In Milestone 1, you explored your data. and came up with research questions. This time, we will finish up our mini data analysis and obtain results for your data by: 

- Making summary tables and graphs 
- Manipulating special data types in R: factors and/or dates and times.
-   Fitting a model object to your data, and extract a result.
-   Reading and writing data as separate files.

We will also explore more in depth the concept of *tidy data.* 

**NOTE**: The main purpose of the mini data analysis is to integrate what you learn in class in an analysis. Although each milestone provides a framework for you to conduct your analysis, it's possible that you might find the instructions too rigid for your data set. If this is the case, you may deviate from the instructions -- just make sure you're demonstrating a wide range of tools and techniques taught in this class.

# Instructions

**To complete this milestone**, edit [this very `.Rmd` file](https://raw.githubusercontent.com/UBC-STAT/stat545.stat.ubc.ca/master/content/mini-project/mini-project-2.Rmd) directly. Fill in the sections that are tagged with `<!--- start your work here--->`.

**To submit this milestone**, make sure to knit this `.Rmd` file to an `.md` file by changing the YAML output settings from `output: html_document` to `output: github_document`. Commit and push all of your work to your mini-analysis GitHub repository, and tag a release on GitHub. Then, submit a link to your tagged release on canvas.

**Points**: This milestone is worth 50 points: 45 for your analysis, and 5 for overall reproducibility, cleanliness, and coherence of the Github submission. 

**Research Questions**: In Milestone 1, you chose two research questions to focus on. Wherever realistic, your work in this milestone should relate to these research questions whenever we ask for justification behind your work. In the case that some tasks in this milestone don't align well with one of your research questions, feel free to discuss your results in the context of a different research question.

# Learning Objectives

By the end of this milestone, you should:

-   Understand what *tidy* data is, and how to create it using `tidyr`.
-   Generate a reproducible and clear report using R Markdown.
-   Manipulating special data types in R: factors and/or dates and times.
-   Fitting a model object to your data, and extract a result.
-   Reading and writing data as separate files.

# Setup

Begin by loading your data and the tidyverse package below:

```{r, message = FALSE}
library(datateachr) # <- might contain the data you picked!
library(tidyverse)
```

# Task 1: Process and summarize your data 

From milestone 1, you should have an idea of the basic structure of your dataset (e.g. number of rows and columns, class types, etc.). Here, we will start investigating your data more in-depth using various data manipulation functions. 

### 1.1 (1 point) 

First, write out the 4 research questions you defined in milestone 1 were. This will guide your work through milestone 2:

<!-------------------------- Start your work below ---------------------------->
1. Is the symmetry and fractal dimension of a tumour related? *These are two tumour attributes I am unfamiliar with that I would be interested in exploring.* 
2. How well can the diagnosis of a tumour be predicted by its radius, texture, smoothness, compactness, concavity, symmetry, and fractal dimension? *I am interested in seeing how accurately a diagnosis can be predicted based on physical attributes of the tumour.*
3. Are the worst values of tumour attributes related? (For example, are smoothness_worst and concavity_worst related?) *Similarly as in research question 1, I am interested in investigating which variables are related.*
4. What is the optimal Logistic regression model to predict diagnosis? *It seems natural and useful to me to seek the best prediction model for this data.*
<!----------------------------------------------------------------------------->

Here, we will investigate your data using various data manipulation and graphing functions.

### 1.2 (8 points)

Now, for each of your four research questions, choose one task from options 1-4 (summarizing), and one other task from 4-8 (graphing). You should have 2 tasks done for each research question (8 total). Make sure it makes sense to do them! (e.g. don't use a numerical variables for a task that needs a categorical variable.). Comment on why each task helps (or doesn't!) answer the corresponding research question.

Ensure that the output of each operation is printed!

Also make sure that you're using dplyr and ggplot2 rather than base R. Outside of this project, you may find that you prefer using base R functions for certain tasks, and that's just fine! But part of this project is for you to practice the tools we learned in class, which is dplyr and ggplot2.

**Summarizing:**

1.  Compute the *range*, *mean*, and *two other summary statistics* of **one numerical variable** across the groups of **one categorical variable** from your data.
2.  Compute the number of observations for at least one of your categorical variables. Do not use the function `table()`!
3.  Create a categorical variable with 3 or more groups from an existing numerical variable. You can use this new variable in the other tasks! *An example: age in years into "child, teen, adult, senior".*
4. Compute the proportion and counts in each category of one categorical variable across the groups of another categorical variable from your data. Do not use the function `table()`!

**Graphing:**

6. Create a graph of your choosing, make one of the axes logarithmic, and format the axes labels so that they are "pretty" or easier to read.
7. Make a graph where it makes sense to customize the alpha transparency.

Using variables and/or tables you made in one of the "Summarizing" tasks: 

8. Create a graph that has at least two geom layers. 
9. Create 3 histograms, with each histogram having different sized bins. Pick the "best" one and explain why it is the best.

Make sure it's clear what research question you are doing each operation for!

<!------------------------- Start your work below ----------------------------->


#### Research Question 1.
Is the symmetry and fractal dimension of a tumour related? 

To investigate this research question, take the variables *symmetry_mean* and *fractal_dimension_mean*. 


**Summarizing:** Compute the *range*, *mean*, and *two other summary statistics* of **one numerical variable** across the groups of **one categorical variable** from your data.
It is logical to compute four summary statistics of both the symmetry and fractal variables in the _**cancer_sample**_ dataset across the groups of the diagnosis variable (malignant and benign). The four summary statistics include: *range*, *mean*, *standard deviation*, and *IQR* (interquartile range).

```{r}
summary_table_1 <- cancer_sample %>% group_by(diagnosis) %>% 
                                      summarise(across(c(symmetry_mean, fractal_dimension_mean), list(min=min, max=max, mean=mean, sd=sd, IQR=IQR))) %>% 
                                      pivot_longer(-diagnosis,
                                                   names_to = c("variable",".value"),
                                                   names_pattern = "(.+)_(.+)")
(summary_table_1)
```


**Graphing:** Create a graph of your choosing, make one of the axes logarithmic, and format the axes labels so that they are “pretty” or easier to read.

This research question asks if symmetry and fractal dimension are related. A plot of these variables will help us visually hypothesize any possible relations. 

```{r}
cancer_sample %>% ggplot(aes(x = symmetry_mean, y = fractal_dimension_mean)) + 
                geom_point()  + scale_y_log10("Log10 Fractal Dimension Mean") + 
                xlab("Symmetry") +
                ggtitle("Log Fractal Dimension vs. Symmetry")
```


#### Research Question 2. 
How well can the diagnosis of a tumour be predicted by its radius, texture, smoothness, compactness, concavity, symmetry, and fractal dimension? Similarly to the first research question, use the *mean* variable for each attribute of the tumour. 

**Summarizing:** Compute the *range*, *mean*, and *two other summary statistics* of **one numerical variable** across the groups of **one categorical variable** from your data. Interest in the predictability of a tumours diagnosis from the variables listed above, it is intuitive to observe their descriptive statistics to see if they each offer varying qualities. 


```{r}
summary_table_2 <- cancer_sample %>% group_by(diagnosis) %>% 
                                    summarise(across(c(radius_mean, texture_mean, smoothness_mean, compactness_mean, concavity_mean, symmetry_mean, fractal_dimension_mean), 
                                                     list(min=min, max=max, mean=mean, sd=sd, IQR=IQR))) %>% 
                                    pivot_longer(-diagnosis,
                                                 names_to = c("variable",".value"),
                                                 names_pattern = "(.+)_(.+)")
(summary_table_2)
```


**Graphing:** Create a graph of your choosing, make one of the axes logarithmic, and format the axes labels so that they are "pretty" or easier to read.

To investigate whether or not a variable may be useful in predicting a cateogrical variable, it is useful to graph a side-by-side boxplot to see if the variable is noticeably different for each class. Using a log-scale will help disregard outliers.

```{r}
cancer_sample %>% ggplot(aes(diagnosis, log(radius_mean), fill=factor(diagnosis))) + geom_boxplot() + xlab("Diagnosis") + ylab("log Radius") + ggtitle("Log-Scaled Radius Boxplot")
cancer_sample %>% ggplot(aes(diagnosis, log(texture_mean), fill=factor(diagnosis))) + geom_boxplot() + xlab("Diagnosis") + ylab("log Texture") + ggtitle("Log-Scaled Radius Boxplot")
cancer_sample %>% ggplot(aes(diagnosis, log(smoothness_mean), fill=factor(diagnosis))) + geom_boxplot() + xlab("Diagnosis") + ylab("log Smoothness") + ggtitle("Log-Scaled Radius Boxplot")
cancer_sample %>% ggplot(aes(diagnosis, log(compactness_mean), fill=factor(diagnosis))) + 
  geom_boxplot() + xlab("Diagnosis") + ylab("log Compactness") + ggtitle("Log-Scaled Radius Boxplot")
cancer_sample %>% ggplot(aes(diagnosis, log(concavity_mean), fill=factor(diagnosis))) + geom_boxplot() + xlab("Diagnosis") + ylab("log Concavity") + ggtitle("Log-Scaled Radius Boxplot")
cancer_sample %>% ggplot(aes(diagnosis, log(symmetry_mean), fill=factor(diagnosis))) + geom_boxplot() + xlab("Diagnosis") + ylab("log Symmetry") + ggtitle("Log-Scaled Radius Boxplot")
cancer_sample %>% ggplot(aes(diagnosis, log(fractal_dimension_mean), fill=factor(diagnosis))) + geom_boxplot() + xlab("Diagnosis") + ylab("log Fractal Dimension") + ggtitle("log Radius Boxplot")
```


#### Research Question 3. 
Are the worst values of tumour attributes related? (For example, are smoothness_worst and concavity_worst related?) 

**Summarizing:** Compute the *range*, *mean*, and *two other summary statistics* of **one numerical variable** across the groups of **one categorical variable** from your data.

Since most variables in the _**cancer_sample**_ dataset are numerical, the summarizing strategy above remains the best choice, especially considering this research questions asks about whether or not these variables are related. 

```{r}
summary_table_3 <- cancer_sample %>% group_by(diagnosis) %>% 
                                      summarise(across(ends_with("_worst"), 
                                                       list(min=min, max=max, mean=mean, sd=sd, IQR=IQR))) %>% 
                                      pivot_longer(-diagnosis,
                                                   names_to = c("variable",".value"),
                                                   names_pattern = "(.+)_(.+)")
(summary_table_3)
```


**Graphing:** Create a graph of your choosing, make one of the axes logarithmic, and format the axes labels so that they are “pretty” or easier to read.

Take a few particular examples of interest, and compare their values in a plot. The y-variable is log-scacled in each plot. It is expected for *perimeter_worst* and *area_worst* to be related, as well as *concavity_worst* and *concave_points_worst*. 

```{r}
cancer_sample %>% ggplot(aes(x = radius_worst, y = texture_worst)) + 
                geom_point()  + scale_y_log10("Log10 Texture Worst") + 
                xlab("Radius Worst") +
                ggtitle("Log Scaled Texture Worst vs. Radius Worst")

cancer_sample %>% ggplot(aes(x = perimeter_worst, y = area_worst)) + 
                geom_point()  + scale_y_log10("Log10 Area Worst") + 
                xlab("Perimeter Worst") +
                ggtitle("Log Scaled Area Worst vs. Perimeter Worst")

cancer_sample %>% ggplot(aes(x = smoothness_worst, y = compactness_worst)) + 
                geom_point()  + scale_y_log10("Log10 Compactness Worst") + 
                xlab("Smoothness Worst") +
                ggtitle("Log Scaled Compactness Worst vs. Smoothness Worst")

cancer_sample %>% ggplot(aes(x = concavity_worst, y = concave_points_worst)) + 
                geom_point()  + scale_y_log10("Log10 Concave Points Worst") + 
                xlab("Concavity Worst") +
                ggtitle("Log Scaled Concave Points Worst vs. Concavity Worst")
```



#### Research Question 4.
What is the optimal Logistic regression model to predict diagnosis? 

**Summarizing:** Compute the number of observations for at least one of your categorical variables.

It is logical to check the number of observations for the diagnoses of the tumours. To find an appropriate Logistic regression model, one would hope for the classes M and D to be relatively balanced and abundant.  

```{r}
summary_table_4 <- cancer_sample %>% group_by(diagnosis) %>% summarise(n = n())
(summary_table_4)
```

It seems 357 observations have a benign diagnosis and 212 observations have a malignant diagnosis.


**Graphing:** Create a graph that has at least two geom layers.

Below is a geom barplot of the count for each class of the diagnosis veriable. Another geom text layer is added. 

```{r}
cancer_sample %>% ggplot(aes(x = diagnosis, fill = diagnosis)) + geom_bar() + geom_text(stat='count', aes(label=after_stat(count)), vjust=-0.4)
```

<!----------------------------------------------------------------------------->

### 1.3 (2 points)

Based on the operations that you've completed, how much closer are you to answering your research questions? Think about what aspects of your research questions remain unclear. Can your research questions be refined, now that you've investigated your data a bit more? Which research questions are yielding interesting results?

<!------------------------- Write your answer here ---------------------------->

Recall the research questions investigated above: 
1. Is the symmetry and fractal dimension of a tumour related? 
2. How well can the diagnosis of a tumour be predicted by its radius, texture, smoothness, compactness, concavity, symmetry, and fractal dimension?
3. Are the worst values of tumour attributes related? (For example, are smoothness_worst and concavity_worst related?)
4. What is the optimal Logistic regression model to predict diagnosis?

Questions 1 and 3 each deal with whether variables the in dataset are related. The question can be answered tentatively using the plots above. A strong linear or non-linear relatinoship may be observed using scattplots, which is seen for variables such as area and perimeter. Further steps may include computing the correlation between variables numerically. 

Research question 2 asks if a subset of variables in the _**cancer_sample**_ dataset may be used to predict the diagnosis of the tumour. The boxplots above are reason to suspect a variable may or may not be useful in predicting the diagnosis variable, but it is difficult to say for certain without building and testing a model. The research question can be refined to instead ask: "Do the descriptive statistics of the radius, texture, smoothness, compactness, concavity, symmetry, and fractal dimension variables vary for each class in the diagnosis variable?". These results are fairly interesting, and may help in further investigation for research question 4. 

Research question 4 is not answered by the summary and graph above. It seems there are sufficient observations to build and test a logistic regression model to predict the diagnosis of a tumour, but there is still much work to be done to answer the original question. 



<!----------------------------------------------------------------------------->

# Task 2: Tidy your data 

In this task, we will do several exercises to reshape our data. The goal here is to understand how to do this reshaping with the `tidyr` package.

A reminder of the definition of *tidy* data:

-   Each row is an **observation**
-   Each column is a **variable**
-   Each cell is a **value**

### 2.1 (2 points)

Based on the definition above, can you identify if your data is tidy or untidy? Go through all your columns, or if you have \>8 variables, just pick 8, and explain whether the data is untidy or tidy.

<!--------------------------- Start your work below --------------------------->
The _**cancer_sample**_ dataset is tidy. Each tumour attribute (e.g., radius, texture, perimeter, etc.) it reflected in multiple variables with three distinct statistics (e.g. radius_mean, radius_se, radius_worst). This allows each row to be an observation, each column to be a distinct variable, and each cell to be a value. Notably, each row represents a unique tumour. 
<!----------------------------------------------------------------------------->

### 2.2 (4 points)

Now, if your data is tidy, untidy it! Then, tidy it back to it's original state.

If your data is untidy, then tidy it! Then, untidy it back to it's original state.

Be sure to explain your reasoning for this task. Show us the "before" and "after".

<!--------------------------- Start your work below --------------------------->

To untidy the data, I will pivot longer to add a categorical variable with levels mean, se, and worst. Each attribute of the tumour will stand alone as one of the following: radius, texture, perimeter, area, smoothness, compactness, concavity, concave_points, symmetry, or fractal dimension. To carry this out, *pivot_longer* will be used on all columns except for ID and diagnosis. Variable names will by spliced on the last underscore in the string. For example, radius_mean will be spliced to be radius (variable name) and mean (statistic value). This is done using a REGEX expression: **(.*)_(.*)**. 

```{r}
cancer_sample_untidy <- cancer_sample %>% pivot_longer(cols = c(-ID, -diagnosis), names_to = c(".value", "statistic"), names_pattern = '(.*)_(.*)')
cancer_sample_untidy
```

This dataset is untidy because each tumour is represented by several rows. In other words, each row is **not** a single observation. To tidy the dataset, it is necessary to picot wider so the each tumour is reflected in a single row. 

```{r}
cancer_sample_tidy <- cancer_sample_untidy %>% pivot_wider(names_from = statistic, values_from = c(-ID, -diagnosis, -statistic)) 
cancer_sample_tidy
```

It is easy to check if _**cancer_sample_tidy**_ contains identicle information is the original dataset _**cancer_sample**_. Based on the work done above, it is expected that the datasets are the same, with columns re-ordered. To test this, the columns are reordered alphabetically and then each cell may be tested. If all cells match between the two re-ordered datasets, then the following will return TRUE. 


```{r}
all(cancer_sample_tidy[,order(names(cancer_sample_tidy))] == cancer_sample[,order(names(cancer_sample))])
```


<!----------------------------------------------------------------------------->

### 2.3 (4 points)

Now, you should be more familiar with your data, and also have made progress in answering your research questions. Based on your interest, and your analyses, pick 2 of the 4 research questions to continue your analysis in the remaining tasks:

<!-------------------------- Start your work below ---------------------------->

1.  *Is the symmetry and fractal dimension of a tumour related?*
2.  *How well can the diagnosis of a tumour be predicted by its radius, texture, smoothness, compactness, concavity, symmetry, and fractal dimension?*

<!----------------------------------------------------------------------------->

Explain your decision for choosing the above two research questions.

<!--------------------------- Start your work below --------------------------->

For research question 1 copied above, it seems reasonable to ask if two variables are related. Each variable is described using three statistics: mean, se, and worst. It is reasonable to ask if each statistics of each tumour is related. This will allow me to better understand these variables, and deduce if they are likley to be related. If they are related, it makes sense to only include one of them in a predictive model. 

For research question 2, it is reasonable to build a model using a small subset of the variables given what was learned in class. Additionally, the ability to predict whether or not a tumour is benign or malignant seems like a powerful and interesting tool.

<!----------------------------------------------------------------------------->

Now, try to choose a version of your data that you think will be appropriate to answer these 2 questions. Use between 4 and 8 functions that we've covered so far (i.e. by filtering, cleaning, tidy'ing, dropping irrelevant columns, etc.).

(If it makes more sense, then you can make/pick two versions of your data, one for each research question.) 

<!--------------------------- Start your work below --------------------------->

I will pick two version of the data for each research question noted in 2.3. Call them _**cancer_sample_1**_ and _**cancer_sample_2**_ for research question 1 and 2 respectively.

```{r}
## Interested in symmetry and fractal dimension, so filter out all unrelated variables. 
cancer_sample_1 <- cancer_sample %>% select(starts_with(c('symmetry', 'fractal_dimension'))) %>% arrange()
cancer_sample_1


## Interested in diagnosis, radius, texture, smoothness, compactness, concavity, symmetry, and fractal dimension. Filter out non-distinct rows in case data is updated. 
## Mutate the diagnosis variable so that the levels are represetned with numerical values. This will help when we apply glm() later. 
cancer_sample_2 <- cancer_sample %>% 
                    arrange() %>% 
                    select(diagnosis, starts_with(c('radius', 'texture', 'smoothness', 'compactness', 'concavity', 'symmetry', 'fractal_dimension'))) %>% 
                    distinct() %>% 
                    mutate(diagnosis = case_when(diagnosis == 'M' ~ 1,
                                                 diagnosis == 'B' ~ 0))
cancer_sample_2


## Four functions used: select(), arrange(), starts_with(), distinct(), mutate(), case_when()
```

<!----------------------------------------------------------------------------->

<!--------------------------- Start your work below --------------------------->

# Task 3: Modelling

## 3.0 (no points)

Pick a research question from 1.2, and pick a variable of interest (we'll call it "Y") that's relevant to the research question. Indicate these.

<!-------------------------- Start your work below ---------------------------->

**Research Question**: How well can the diagnosis of a tumour be predicted by its radius, texture, smoothness, compactness, concavity, symmetry, and fractal dimension?

**Variable of interest**: diagnosis

<!----------------------------------------------------------------------------->

## 3.1 (3 points)

Fit a model or run a hypothesis test that provides insight on this variable with respect to the research question. Store the model object as a variable, and print its output to screen. We'll omit having to justify your choice, because we don't expect you to know about model specifics in STAT 545.

-   **Note**: It's OK if you don't know how these models/tests work. Here are some examples of things you can do here, but the sky's the limit.

    -   You could fit a model that makes predictions on Y using another variable, by using the `lm()` function.
    -   You could test whether the mean of Y equals 0 using `t.test()`, or maybe the mean across two groups are different using `t.test()`, or maybe the mean across multiple groups are different using `anova()` (you may have to pivot your data for the latter two).
    -   You could use `lm()` to test for significance of regression coefficients.

<!-------------------------- Start your work below ---------------------------->

The following code builds a logistic regression model to predict the diagnosis of a tumour using the variables in _**cancer_sample_2**_. First the data is split into a training and testing set. 

```{r}
## For reproducibility
set.seed(123)
train_ind <- sample(seq_len(nrow(cancer_sample_2)), size = floor(0.7 * nrow(cancer_sample_2)))
cancer_sample_train <- cancer_sample_2 %>% slice(train_ind)
cancer_sample_test <- cancer_sample_2 %>% slice(-train_ind)


cancer_model <- glm(diagnosis ~ ., data = cancer_sample_train, family = "binomial")
(cancer_model)
```

<!----------------------------------------------------------------------------->

## 3.2 (3 points)

Produce something relevant from your fitted model: either predictions on Y, or a single value like a regression coefficient or a p-value.

-   Be sure to indicate in writing what you chose to produce.
-   Your code should either output a tibble (in which case you should indicate the column that contains the thing you're looking for), or the thing you're looking for itself.
-   Obtain your results using the `broom` package if possible. If your model is not compatible with the broom function you're needing, then you can obtain your results by some other means, but first indicate which broom function is not compatible.



<!-------------------------- Start your work below ---------------------------->



The following code uses the predict() function to make predictions on Y (diagnosis). This satisfies the original research question, to investigate if the diangosis of a tumour may be predicted using its characteristics. To visualize the results, add the predictions to a new dataset, _**cancer_predictions**_ dataset and plot. 

```{r}
predictions_list <- predict(cancer_model, newdata = cancer_sample_test, type = "response")
cancer_predictions <- cancer_sample_test %>% select(diagnosis) %>% 
                                        mutate(predictions = predictions_list, 
                                               index = 1:nrow(.), 
                                               correct = case_when(predictions >= 0.5 & diagnosis == 1 ~ TRUE,
                                                                   predictions >= 0.5 & diagnosis == 0 ~ FALSE,
                                                                   predictions < 0.5 & diagnosis == 0 ~ TRUE,
                                                                   predictions < 0.5 & diagnosis == 1 ~ FALSE
                                                                   )) %>% 
                                        select(index, everything()) 
                      

cancer_predictions %>% ggplot(aes(x=index, y=predictions, color = correct)) + geom_point() + ggtitle("Cancer Predictions Plot") + xlab("Index") + ylab("Prediction")
```
<!----------------------------------------------------------------------------->

# Task 4: Reading and writing data

Get set up for this exercise by making a folder called `output` in the top level of your project folder / repository. You'll be saving things there.

## 4.1 (3 points)

Take a summary table that you made from Task 1, and write it as a csv file in your `output` folder. Use the `here::here()` function.

-   **Robustness criteria**: You should be able to move your Mini Project repository / project folder to some other location on your computer, or move this very Rmd file to another location within your project repository / folder, and your code should still work.
-   **Reproducibility criteria**: You should be able to delete the csv file, and remake it simply by knitting this Rmd file.

<!-------------------------- Start your work below ---------------------------->

Choose the second summary table from Task 1. If the file already exists in the output folder, the following code will delete it before a new file is written. 

```{r}
## Check if file exists, delete if it does
if (file.exists(here::here("output/summary_table_2.csv"))) {file.remove(here::here("output/summary_table_2.csv"))}

## Write file
write_csv(summary_table_2, here::here("output/summary_table_2.csv"))
```
<!----------------------------------------------------------------------------->

## 4.2 (3 points)

Write your model object from Task 3 to an R binary file (an RDS), and load it again. Be sure to save the binary file in your `output` folder. Use the functions `saveRDS()` and `readRDS()`.

-   The same robustness and reproducibility criteria as in 4.1 apply here.

<!-------------------------- Start your work below ---------------------------->
```{r}
## Check if file exists, delete if it does
if (file.exists(here::here("output/cancer_model.RDS"))) {file.remove(here::here("output/cancer_model.RDS"))}

## Save file
saveRDS(cancer_model, here::here("output/cancer_model.RDS"))

## Load file
cancer_model <- readRDS(here::here("output/cancer_model.RDS"))
```
<!----------------------------------------------------------------------------->

# Overall Reproducibility/Cleanliness/Coherence Checklist 

Here are the criteria we're looking for.

## Coherence (0.5 points)

The document should read sensibly from top to bottom, with no major continuity errors. 

The README file should still satisfy the criteria from the last milestone, i.e. it has been updated to match the changes to the repository made in this milestone. 

## File and folder structure (1 points)

You should have at least three folders in the top level of your repository: one for each milestone, and one output folder. If there are any other folders, these are explained in the main README.

Each milestone document is contained in its respective folder, and nowhere else.

Every level-1 folder (that is, the ones stored in the top level, like "Milestone1" and "output") has a `README` file, explaining in a sentence or two what is in the folder, in plain language (it's enough to say something like "This folder contains the source for Milestone 1").

## Output (1 point)

All output is recent and relevant:

-   All Rmd files have been `knit`ted to their output md files. 
-   All knitted md files are viewable without errors on Github. Examples of errors: Missing plots, "Sorry about that, but we can't show files that are this big right now" messages, error messages from broken R code
-   All of these output files are up-to-date -- that is, they haven't fallen behind after the source (Rmd) files have been updated.
-   There should be no relic output files. For example, if you were knitting an Rmd to html, but then changed the output to be only a markdown file, then the html file is a relic and should be deleted.

Our recommendation: delete all output files, and re-knit each milestone's Rmd file, so that everything is up to date and relevant.

## Tagged release (0.5 point)

You've tagged a release for Milestone 2. 

### Attribution

Thanks to Victor Yuan for mostly putting this together.
